Inference using context-dependent models of mutation via bounds on information propagation

### 2021-12-11 writeups/context-dependence.tex
github

% TODO include github information

@@

>>>>

@@

%%%%%%%
\section{Software}

The methods described here
are implemented in R
and freely available at \url{https://github.com/petrelharp/context}.
The core implementation of T-mer counting and likelihood evaluation
is provided in an R package, \texttt{contextual},
and is supplemented by (documented) code to simulate from context-dependent models
and perform maximum likelihood or Bayesian inference.
